Deep Learning

### 2015-01-11 deepreview.tex
fixed eqn 2, assuming the missing defn was of tanh

Deep learning is currently making major advances in solving problems that
have resisted the best attempts of the Artificial Intelligence community
for many years. Deep learning is very good at discovering intricate
structure in large, high-dimensional datasets and is therefore widely
applicable in all of the sciences. For example, it has beaten previous
machine learning techniques at predicting the activity of potential drug
molecules~\cite{Dahl}, detecting new fundamental particles~\cite{particles},
classifying galaxies~\cite{??}, or predicting the effects of mutations in
non-coding DNA on gene expression and disease~\cite{Frey}.

So far, most applications of deep learning use feed-forward neural
networks, but for tasks that involve sequential inputs it is often better
to use recurrent neural networks. These are given one element from an input % YB term-->element
sequence at each time step and their recurrent internal ``hidden'' state
depends on the whole history of the input sequence. Recurrent networks are
very good at predicting the next character in a string~\citep{Sutskever-et-al-ICML2011} or
the next word in a sequence~\citep{Mikolov-et-al-NIPS2013} but they can also be used for
more complex tasks.  After reading an English sentence one word at a time,
for example, an English``encoder'' network can be trained so that the final
state vector of its hidden neurons is a good representation of the thought
expressed by the sentence.  This thought vector can then be used as the
initial hidden state of a trained French ``decoder'' network which outputs
a probability distribution for the first word of the French translation. If
a particular first word is chosen (e.g., according to that probability)
and provided as input to the decoder
network it will then output a probability distribution for the second word
of the translation and so on until a full stop is 
chosen~\cite{Vinyals-et-al-arxiv2014,Bahdanau-et-al-arxiv2014}. 
%YB added a clarification
Overall, this process generates sequences of French words according to
a probability distribution that depends on the English sentence.

This rather naive way of performing machine translation has quickly become
competitive with the state-of-the-art and this raises serious doubts about
whether understanding a sentence requires anything like internal symbolic
expressions that are manipulated by binding their symbols to the variables
in judiciously chosen rules of inference.  The encoder-decoder translation
networks do not work by using internal rules of inference in which
variables get bound to symbols. They just use big state vectors, big weight
matrices and scalar non-linearities to get the job done.  This suggests
that deriving conclusions using only the form of the premises is a powerful
technique that people can eventually master but it is not a good model of
the way we normally reason or understand language. Recurrent neural
networks that represent thoughts as big vectors are more compatible with
the view that everyday reasoning involves many simultaneous analogies that
each contribute plausibility to a conclusion\cite{metaphors}.

@@

However, even with good hand-crafted features, many interesting tasks
cannot be solved by linear classifiers. A common method to get around this
problem is to transform the feature vector into a higher dimensional vector
through a non-linear mapping, exploiting the fact that collections of
vectors are more likely to be easily separated when they are spread around
a high-dimensional space~\cite{Cover65}. In the limit when there are at least
as many dimensions as examples, a linear classifier can always separate the
training examples, and one clever way to obtain a very high-dimensional space is to use a
``kernel function'' that measures the similarity between two vectors.
Using the kernel function, any input vector, ${\bf x}_i$ in the training
set can be used to define a feature whose activation for a new input
vector, ${\bf x}_{\rm new}$ is just the similarity between ${\bf x}_i$ and
${\bf x}_{\rm new}$. Given a kernel function, it is possible to jointly
optimize the choice of training inputs used to define features and the
class-specific weights associated with the features~\cite{Boser92}. The training
inputs used to define features are called ``support vectors'' and Support
Vector Machines~\citep{Boser92} have been very successful, especially for
tasks with a relatively small number of training examples in which features
are individually informative. They do not, however, perform well for tasks
such as object recognition in which the input space is high-dimensional and
the input-output mapping is so complex that computing similarities with a
simple kernel function is ineffective.

@@

From the earliest days of pattern recognition~\cite{selfridge,Rosenblatt57}
researchers aimed to replace hand-engineered features by multiple layers of
learned features.  This was eventually achieved by using the
backpropagation algorithm which was discovered independently by several
different groups in the 1970s and 1980s~\citep{Werbos74,Parker85,LeCun85,Rumelhart86b,schmidreference}.  
Backpropagation is simply an application of
the chain rule, which yields an efficient way of computing the gradient of a
smooth objective function with respect to all of the weights in a layered
network. The objective function typically measures the discrepancy between
the actual output of the network on a given training case and the target
output for that case.  The key insight is that the error derivatives with
respect to the {\it outputs} of a layer can be computed by working
backwards from the error derivatives with respect to the outputs of the
subsequent layer. Once this backwards recursion has been used to compute
error derivatives for the outputs of all layers, it is easy to compute
error derivatives for the parameters (or weights) of each layer (see box
1).

@@

Backpropagation provides an efficient way of computing gradients for all of
the weights in a layered network on a single training case, but there are
still many ways to make use of these gradients. The most obvious method is
to average the gradients over all of the cases in the training set and then
to change each weight in proportion to its negative gradient, which is the
direction where a small change will most improve the objective function. 
When the training set contains millions of cases and is highly redundant, however,
this is needlessly slow. It is much faster to compute the average gradient
on a small ``mini-batch'' of randomly chosen training cases and to update
each weight by this stochastic estimate of its full gradient times a
learning rate which decays as learning proceeds. Stochastic gradient
descent can be improved by using the history of the individual weight
gradients to adapt the learning rate for each weight~\citep{bottou-bousquet-2008-small}
or to provide additional increments that depend on earlier gradients~\cite{momentum}
but these techniques are still the subject of controversy and are beyond
the scope of this review.  However, it is now widely accepted that some
form of stochastic gradient descent is the best bet for large, redundant
datasets.

@@

The hidden layers of a multi-layer neural network learn to represent the
network's inputs in a way that makes it easy to predict the target
outputs. This is nicely demonstrated by training a multi-layer neural
network to predict the next word in a sequence from a local context of
earlier words~\citep{BenDucVin01-short}. 
Each context word is presented to the network as a one-of-N
vector in which one component has a value of $1$ and the rest are $0$. The
output layer has one unit per word and is forced to produce a probability
distribution over words by using the ``softmax'' function:
\begin{equation}
p_j = \frac{exp(z_j)}{\sum_i exp(z_i)}
\end{equation}
where $z_j$ is the total input received by output unit $j$. The hidden
layers use either the logistic or tanh non-linearity:
\begin{equation}
y_j = \frac{1}{1+ \exp(z_j)}, \ \ \ y_j = \frac{}{} % YB: what was the intent here for the 2nd part?
\end{equation}

The connectivity of the network is restricted so that each of the one-of-N
input vectors must first be converted to a ``word-vector'' before being
used by subsequent layers to give a high probability to the target next
word.  The network learns word-vectors that contain many active components
each of which can be interpreted as a separate feature of the word. This
was first demonstrated\cite{RHW} using sequences of three words, such as
(Colin, Mother, Victoria), derived from two family trees. The learned word
vector for Colin contained ``semantic'' features representing which family
tree Colin was in, what branch of that tree he was in, and from what generation
he was~\citep{Hinton-et-al-PDP1986}. These semantic features were not explicitly present
in the input.  They were discovered by the learning procedure as a good way
of factorizing the structured relationships between the input and output
symbols into multiple ``micro-rules''.  For example, given Colin's
generation and the learned feature of Mother that the output should be one
generation higher than the input, we can already restrict the answer to
people in a specific generation. The ability of deep learning to discover
many such micro-rules allows it to generalize well to novel combinations of
individually familiar context words.

@@

Interest in deep feed-forward networks was revived in
2005 and 2006~\citep{IJCAI,Hinton06-small,Bengio-nips-2006-small,ranzato-07-small} 
by the introduction
of unsupervised learning procedures that could create layers of feature
detectors without requiring labeled data. The objective in learning each
layer of feature detectors was to be able to reconstruct or model the
activities of feature detectors (or raw inputs) in the layer below.  By
``pre-training'' several layers of progressively more complex feature
detectors using this reconstruction objective, the weights of a deep
network could be initialized to sensible values.  A final layer of output
units could then be added to the top of the network and the whole deep
system could be fine-tuned using standard
backpropagation\cite{Hinton-Science2006}. This worked remarkably well for recognizing
handwritten digits especially when the amount of labeled data was very
limited~\citep{Bengio-nips-2006-small,Erhan+al-2010-small}.

The first major application of this pre-training approach was in speech
recognition and it was made possible by the advent of fast Graphics
Processing Units (GPUs) that were convenient to program~\citep{RainaICML09-small}.  
In 2009, the approach was used to map short temporal windows of coefficients extracted
from a soundwave to a set of probabilities for the various fragments of
speech that might be represented by the frame in the center of the window.
It achieved record-breaking results on a standard speech recognition
benchmark that used a small vocabulary\cite{TIMITpaper} and was quickly
developed to give record-breaking results on a large vocabulary
task~\cite{Dahl}.  By 2012, versions of the deep net from 2009 were being
developed by many of the major speech groups\cite{Hinton-et-al-2012} and were already
being deployed in Android phones.  For smaller datasets, unsupervised
pre-training helps to prevent overfitting~\citep{Erhan+al-2010-small}, 
leading to significantly better generalization when the number of
labeled examples is small. Once deep
learning had been rehabilitated, it turned out that large labeled datasets
did not need the pre-training stage, provided the scales of the initial
random weights were carefully chosen to avoid very large or very small
initial gradients.

@@

When LSTMs were first described in
English~\citep{Hochreiter+Schmidhuber-1997} their complexity was off-putting
and, despite their impressive ability to learn very long-range temporal
structure on toy problems, they were largely ignored until they achieved
excellent results in a competition to read cursive
hand-writing~\cite{Graves-et-al-2009}. They have subsequently proved to be very
effective for tasks that have sequential input.  They are now better than
deep feed-forward networks for speech recognition~\cite{gravestimit} and
unlike feed-forward nets they can implement an entire speech recognition
system that goes all the way from coefficents derived from the soundwave to
the sequence of characters in the transcription~\cite{gravestimit}.  They
are also what is currently used for the encoder and decoder networks that
perform so well at machine
translation~\citep{Bahdanau-et-al-arxiv2014,Sutskever-et-al-NIPS2014}.

Recent work~\citep{Chung-et-al-NIPSDL2014} suggests that not all the elements of the LSTM
architecture are required, the crucial element being the presence of
of the gate controlling the leaking rate (or time constant) of the cell.
%It is not yet clear which aspects of the complicated architecture of LSTMs
%are really necessary. Memory cells are a good way of allowing the
%backpropagated error derivatives to neither explode nor vanish, but they
%are not the only way.  For example, recurrent nets with rectified linear
%hidden units that use the non-linear function $y=max(0,x)$ are much simpler
%than LSTMs and if the recurrent weight matrix is initialized to be close to
%the identity matrix they work about as well as LSTMs both for toy problems
%involving very long-range temporal structure and for real tasks like
%predicting the next word in text\cite{LeHinton}.

@@

When translating between languages, the hidden units of the decoder network
that generates possible translations are initialized with a ``thought
vector'' which is the final hidden state of an encoder network.  But it is
also possible to initialize a decoder network using a linear transformation
of the last hidden layer of a deep convolutonal network that has already
been trained to recognize objects in images. The decoder network can then
be trained by BPTT on a dataset of captioned
images~\cite{NIC,StanfordNIC,more?} and it produces remarkably good
captions (see Figure~\ref{fig:caption-generation}).

@@

Learning which action will maximize the total future reward given a state
of the world is difficult when the rewards are delayed and the world has a
very large number of possible states. One impressive recent development is
a single system that can learn to play many different video
games~\cite{Deepmind-atari-arxiv2013}. The system uses a deep convolutional network to
map from the pixels on the screen at several previous time steps to the
expected future reward of each possible action and its only inputs are the
pixels and the current score in the game. The learning works by minimizing
the difference between the system's current estimate of future reward and a
noisy but less biased estimate that is obtained by using the same deep
network to estimate the future reward of the next state, where the next
state is chosen stochastically based on the predicted future rewards of all
the currently legal actions.

@@

Human vision is an active process in which intelligent fixations are used
to ensure that only a tiny fraction of the optic array is ever processed at
high resolution. We expect much of the future progress in vision,
especially for video understanding or robotics, to come from systems that
are trained end-to-end and combine deep convolutional networks with
recurrent nets that use reinforcement learning to decide where to
look\cite{}.  Such systems already outperform passive vision
systems\cite{ba+mnih}.  Similarly, when understanding sentences or whole
documents we expect future systems to learn strategies for selectively
attending to one part at a time~\cite{Bahdanau-et-al-arxiv2014}. We also expect
that in the next few years deep recurrent neural networks will become far
better at understanding the meaning of documents, including the way in
which the thoughts expressed by the sentences are related to one another.

This review has focused on supervised learning because of its recent
achievements and we have ignored much interesting work on unsupervised
learning procedures for deep neural 
networks~\citep{Salakhutdinov2009-small,wake-sleep,
  google-cat, denoising-auto, ranzato-pami, more recent}. In the long run,
however, we believe unsupervised learning will be essential for allowing
deep networks to generalize well by creating internal representations that
untangle the many different factors that interact to produce images, speech
and documents~\cite{Yann,Bengio-Courville-Vincent-TPAMI2013}.

@@

\iffalse

@@

%Krizhevsky, A., Sutskever, I., \& Hinton, G. E. (2012)\\ Imagenet
%classification with deep convolutional neural networks.\\ In Advances in
%Neural Information Processing Systems (1097-1105).
% --> \cite{Krizhevsky-2012-small}

@@

%\fi

@@

2. Maps showing:\\ a) that word vectors learned by backpropagation are very
good at capturing the meanings of the words.\\ b) that the thought vectors
extracted by a translation model are very good at capturing the thoughts
expressed by sentences.

@@

4. Some images with:\\ a) The opinions of a deep convolutional net about
the classes of the prominent objects.\\ b) Several alternative captions
generated by using the output of the convolutional net to determine the
initial hidden state of a decoder recurrent net.

>>>>

Deep learning is currently making major advances in solving problems that
have resisted the best attempts of the Artificial Intelligence community
for many years. Deep learning is very good at discovering intricate
structure in large, high-dimensional datasets and is therefore widely
applicable in all of the sciences. For example, it has beaten previous
machine learning techniques at predicting the activity of potential drug
molecules~\citep{Dahl}, detecting new fundamental particles~\citep{particles},
classifying galaxies~\citep{??}, or predicting the effects of mutations in
non-coding DNA on gene expression and disease~\citep{Frey}.

So far, most applications of deep learning use feed-forward neural
networks, but for tasks that involve sequential inputs it is often better
to use recurrent neural networks. These are given one element from an input % YB term-->element
sequence at each time step and their recurrent internal ``hidden'' state
depends on the whole history of the input sequence. Recurrent networks are
very good at predicting the next character in a string~\citep{Sutskever-et-al-ICML2011} or
the next word in a sequence~\citep{Mikolov-et-al-NIPS2013} but they can also be used for
more complex tasks.  After reading an English sentence one word at a time,
for example, an English``encoder'' network can be trained so that the final
state vector of its hidden neurons is a good representation of the thought
expressed by the sentence.  This thought vector can then be used as the
initial hidden state of a trained French ``decoder'' network which outputs
a probability distribution for the first word of the French translation. If
a particular first word is chosen (e.g., according to that probability)
and provided as input to the decoder
network it will then output a probability distribution for the second word
of the translation and so on until a full stop is 
chosen~\citep{Vinyals-et-al-arxiv2014,Bahdanau-et-al-arxiv2014}. 
%YB added a clarification
Overall, this process generates sequences of French words according to
a probability distribution that depends on the English sentence.

This rather naive way of performing machine translation has quickly become
competitive with the state-of-the-art and this raises serious doubts about
whether understanding a sentence requires anything like internal symbolic
expressions that are manipulated by binding their symbols to the variables
in judiciously chosen rules of inference.  The encoder-decoder translation
networks do not work by using internal rules of inference in which
variables get bound to symbols. They just use big state vectors, big weight
matrices and scalar non-linearities to get the job done.  This suggests
that deriving conclusions using only the form of the premises is a powerful
technique that people can eventually master but it is not a good model of
the way we normally reason or understand language. Recurrent neural
networks that represent thoughts as big vectors are more compatible with
the view that everyday reasoning involves many simultaneous analogies that
each contribute plausibility to a conclusion~\citep{metaphors}.

@@

However, even with good hand-crafted features, many interesting tasks
cannot be solved by linear classifiers. A common method to get around this
problem is to transform the feature vector into a higher dimensional vector
through a non-linear mapping, exploiting the fact that collections of
vectors are more likely to be easily separated when they are spread around
a high-dimensional space~\citep{Cover65}. In the limit when there are at least
as many dimensions as examples, a linear classifier can always separate the
training examples, and one clever way to obtain a very high-dimensional space is to use a
``kernel function'' that measures the similarity between two vectors.
Using the kernel function, any input vector, ${\bf x}_i$ in the training
set can be used to define a feature whose activation for a new input
vector, ${\bf x}_{\rm new}$ is just the similarity between ${\bf x}_i$ and
${\bf x}_{\rm new}$. Given a kernel function, it is possible to jointly
optimize the choice of training inputs used to define features and the
class-specific weights associated with the features~\citep{Boser92}. The training
inputs used to define features are called ``support vectors'' and Support
Vector Machines~\citep{Boser92} have been very successful, especially for
tasks with a relatively small number of training examples in which features
are individually informative. They do not, however, perform well for tasks
such as object recognition in which the input space is high-dimensional and
the input-output mapping is so complex that computing similarities with a
simple kernel function is ineffective.

@@

From the earliest days of pattern recognition~\citep{selfridge,Rosenblatt57}
researchers aimed to replace hand-engineered features by multiple layers of
learned features.  This was eventually achieved by using the
backpropagation algorithm which was discovered independently by several
different groups in the 1970s and 1980s~\citep{Werbos74,Parker85,LeCun85,Rumelhart86b,schmidreference}.  
Backpropagation is simply an application of
the chain rule, which yields an efficient way of computing the gradient of a
smooth objective function with respect to all of the weights in a layered
network. The objective function typically measures the discrepancy between
the actual output of the network on a given training case and the target
output for that case.  The key insight is that the error derivatives with
respect to the {\it outputs} of a layer can be computed by working
backwards from the error derivatives with respect to the outputs of the
subsequent layer. Once this backwards recursion has been used to compute
error derivatives for the outputs of all layers, it is easy to compute
error derivatives for the parameters (or weights) of each layer (see box
1).

@@

Backpropagation provides an efficient way of computing gradients for all of
the weights in a layered network on a single training case, but there are
still many ways to make use of these gradients. The most obvious method is
to average the gradients over all of the cases in the training set and then
to change each weight in proportion to its negative gradient, which is the
direction where a small change will most improve the objective function. 
When the training set contains millions of cases and is highly redundant, however,
this is needlessly slow. It is much faster to compute the average gradient
on a small ``mini-batch'' of randomly chosen training cases and to update
each weight by this stochastic estimate of its full gradient times a
learning rate which decays as learning proceeds. Stochastic gradient
descent can be improved by using the history of the individual weight
gradients to adapt the learning rate for each weight~\citep{bottou-bousquet-2008-small}
or to provide additional increments that depend on earlier gradients~\citep{momentum}
but these techniques are still the subject of controversy and are beyond
the scope of this review.  However, it is now widely accepted that some
form of stochastic gradient descent is the best bet for large, redundant
datasets.

@@

The hidden layers of a multi-layer neural network learn to represent the
network's inputs in a way that makes it easy to predict the target
outputs. This is nicely demonstrated by training a multi-layer neural
network to predict the next word in a sequence from a local context of
earlier words~\citep{BenDucVin01-short}. 
Each context word is presented to the network as a one-of-N
vector in which one component has a value of $1$ and the rest are $0$. The
output layer has one unit per word and is forced to produce a probability
distribution over words by using the ``softmax'' function:
\begin{equation}
p_j = \frac{e^{z_j}}{\sum_i e^{z_i}}
\end{equation}
where $z_j$ is the total input received by output unit $j$. The hidden
layers use either the logistic or tanh non-linearity, respectively:
\begin{equation}
y_j = \frac{1}{1+ e^{z_j}}, \ \ \ y_j = \frac{e^{z_j}-e^{-z_j}}{e^{z_j}+e^{-z_j}} % YB: what was the intent here for the 2nd part?
\end{equation}

The connectivity of the network is restricted so that each of the one-of-N
input vectors must first be converted to a ``word-vector'' before being
used by subsequent layers to give a high probability to the target next
word.  The network learns word-vectors that contain many active components
each of which can be interpreted as a separate feature of the word. This
was first demonstrated~\citep{RHW} using sequences of three words, such as
(Colin, Mother, Victoria), derived from two family trees. The learned word
vector for Colin contained ``semantic'' features representing which family
tree Colin was in, what branch of that tree he was in, and from what generation
he was~\citep{Hinton-et-al-PDP1986}. These semantic features were not explicitly present
in the input.  They were discovered by the learning procedure as a good way
of factorizing the structured relationships between the input and output
symbols into multiple ``micro-rules''.  For example, given Colin's
generation and the learned feature of Mother that the output should be one
generation higher than the input, we can already restrict the answer to
people in a specific generation. The ability of deep learning to discover
many such micro-rules allows it to generalize well to novel combinations of
individually familiar context words.

@@

Interest in deep feed-forward networks was revived in
2005 and 2006~\citep{IJCAI,Hinton06-small,Bengio-nips-2006-small,ranzato-07-small} 
by the introduction
of unsupervised learning procedures that could create layers of feature
detectors without requiring labeled data. The objective in learning each
layer of feature detectors was to be able to reconstruct or model the
activities of feature detectors (or raw inputs) in the layer below.  By
``pre-training'' several layers of progressively more complex feature
detectors using this reconstruction objective, the weights of a deep
network could be initialized to sensible values.  A final layer of output
units could then be added to the top of the network and the whole deep
system could be fine-tuned using standard
backpropagation\citep{Hinton-Science2006}. This worked remarkably well for recognizing
handwritten digits especially when the amount of labeled data was very
limited~\citep{Bengio-nips-2006-small,Erhan+al-2010-small}.

The first major application of this pre-training approach was in speech
recognition and it was made possible by the advent of fast Graphics
Processing Units (GPUs) that were convenient to program~\citep{RainaICML09-small}.  
In 2009, the approach was used to map short temporal windows of coefficients extracted
from a soundwave to a set of probabilities for the various fragments of
speech that might be represented by the frame in the center of the window.
It achieved record-breaking results on a standard speech recognition
benchmark that used a small vocabulary~\citep{TIMITpaper} and was quickly
developed to give record-breaking results on a large vocabulary
task~\citep{Dahl}.  By 2012, versions of the deep net from 2009 were being
developed by many of the major speech groups\citep{Hinton-et-al-2012} and were already
being deployed in Android phones.  For smaller datasets, unsupervised
pre-training helps to prevent overfitting~\citep{Erhan+al-2010-small}, 
leading to significantly better generalization when the number of
labeled examples is small. Once deep
learning had been rehabilitated, it turned out that large labeled datasets
did not need the pre-training stage, provided the scales of the initial
random weights were carefully chosen to avoid very large or very small
initial gradients.

@@

When LSTMs were first described in
English~\citep{Hochreiter+Schmidhuber-1997} their complexity was off-putting
and, despite their impressive ability to learn very long-range temporal
structure on toy problems, they were largely ignored until they achieved
excellent results in a competition to read cursive
hand-writing~\citep{Graves-et-al-2009}. They have subsequently proved to be very
effective for tasks that have sequential input.  They are now better than
deep feed-forward networks for speech recognition~\citep{gravestimit} and
unlike feed-forward nets they can implement an entire speech recognition
system that goes all the way from coefficents derived from the soundwave to
the sequence of characters in the transcription~\citep{gravestimit}.  They
are also what is currently used for the encoder and decoder networks that
perform so well at machine
translation~\citep{Bahdanau-et-al-arxiv2014,Sutskever-et-al-NIPS2014}.

Recent work~\citep{Chung-et-al-NIPSDL2014} suggests that not all the elements of the LSTM
architecture are required, the crucial element being the presence of
of the gate controlling the leaking rate (or time constant) of the cell.
%It is not yet clear which aspects of the complicated architecture of LSTMs
%are really necessary. Memory cells are a good way of allowing the
%backpropagated error derivatives to neither explode nor vanish, but they
%are not the only way.  For example, recurrent nets with rectified linear
%hidden units that use the non-linear function $y=max(0,x)$ are much simpler
%than LSTMs and if the recurrent weight matrix is initialized to be close to
%the identity matrix they work about as well as LSTMs both for toy problems
%involving very long-range temporal structure and for real tasks like
%predicting the next word in text\citep{LeHinton}.

@@

When translating between languages, the hidden units of the decoder network
that generates possible translations are initialized with a ``thought
vector'' which is the final hidden state of an encoder network.  But it is
also possible to initialize a decoder network using a linear transformation
of the last hidden layer of a deep convolutonal network that has already
been trained to recognize objects in images. The decoder network can then
be trained by BPTT on a dataset of captioned
images~\citep{NIC,StanfordNIC,more?} and it produces remarkably good
captions (see Figure~\ref{fig:caption-generation}).

@@

Learning which action will maximize the total future reward given a state
of the world is difficult when the rewards are delayed and the world has a
very large number of possible states. One impressive recent development is
a single system that can learn to play many different video
games~\citep{Deepmind-atari-arxiv2013}. The system uses a deep convolutional network to
map from the pixels on the screen at several previous time steps to the
expected future reward of each possible action and its only inputs are the
pixels and the current score in the game. The learning works by minimizing
the difference between the system's current estimate of future reward and a
noisy but less biased estimate that is obtained by using the same deep
network to estimate the future reward of the next state, where the next
state is chosen stochastically based on the predicted future rewards of all
the currently legal actions.

@@

Human vision is an active process in which intelligent fixations are used
to ensure that only a tiny fraction of the optic array is ever processed at
high resolution. We expect much of the future progress in vision,
especially for video understanding or robotics, to come from systems that
are trained end-to-end and combine deep convolutional networks with
recurrent nets that use reinforcement learning to decide where to
look~\citep{rl+attention}.  Such systems already outperform passive vision
systems~\citep{ba+mnih}.  Similarly, when understanding sentences or whole
documents we expect future systems to learn strategies for selectively
attending to one part at a time~\citep{Bahdanau-et-al-arxiv2014}. We also expect
that in the next few years deep recurrent neural networks will become far
better at understanding the meaning of documents, including the way in
which the thoughts expressed by the sentences are related to one another.

This review has focused on supervised learning because of its recent
achievements and we have ignored much interesting work on unsupervised
learning procedures for deep neural 
networks~\citep{Salakhutdinov2009-small,wake-sleep,
  google-cat, denoising-auto, ranzato-pami, more recent}. In the long run,
however, we believe unsupervised learning will be essential for allowing
deep networks to generalize well by creating internal representations that
untangle the many different factors that interact to produce images, speech
and documents~\citep{Yann,Bengio-Courville-Vincent-TPAMI2013}.

@@

@@

%Krizhevsky, A., Sutskever, I., \& Hinton, G. E. (2012)\\ Imagenet
%classification with deep convolutional neural networks.\\ In Advances in
%Neural Information Processing Systems (1097-1105).
% --> \citep{Krizhevsky-2012-small}

@@

@@

DONE 2. Maps showing:\\ a) that word vectors learned by backpropagation are very
good at capturing the meanings of the words.\\ b) that the thought vectors
extracted by a translation model are very good at capturing the thoughts
expressed by sentences.

@@

4. Some images with:\\ a) The opinions of a deep convolutional net about
the classes of the prominent objects.\\ 
DONE b) Several alternative captions
generated by using the output of the convolutional net to determine the
initial hidden state of a decoder recurrent net.
